---
title: "inventory prediction"
format: 
  html:
    code-fold: true
editor: visual
---

```{r include=FALSE}
setwd("~/gvsu/summer 23/stat 631/Collection/sections/glmv1")

if (!require("pacman")) {
  install.packages("pacman")
  library("pacman")
}
#Import Libraries

# Use p_load() to install (if necessary) and load  packages
pacman::p_load(tidyverse,
               tidymodels,
               leaps,
               corrplot,
               MMWRweek) # for subset selection
```

```{r}
# import data
sai <-  read.csv("inventory.csv")
```

DRAFT DRAFT OUTLINE

## Clear Description of Data:

Start by providing a comprehensive summary of the dataset. This includes source information, timeframe, and the main purpose for collection. Each variable should be properly named and described. This could be presented in the form of a data dictionary.

\[insert\]

## Statistical Summary:

Provide a statistical summary of the variables. This includes measures of central tendency (mean, median, mode), dispersion (range, standard deviation, variance), and distribution properties (skewness, kurtosis). This could be supplemented with summary tables and histograms.

\[insert\]

## Visual Exploration:

Use visualizations to give an overview of the data. Histograms, box plots, scatter plots, or correlation heatmaps can be used to show relationships and trends within the data..

\[insert\]

## Initial Insights:

Start by providing a comprehensive summary of the dataset. This includes source information, timeframe, and the main purpose for collection. Each variable should be properly named and described. This could be presented in the form of a data dictionary.

\[insert\]

# Feature engineering

(link to data dictionary)

-   totals for each item over the year
-   which items are best selling? top ten items based on volume
-   convert weeks to dates so we can extract the month
-   lag period for seasonality
-   rolling mean

```{r}

# total yearly sales for each item
inventory_sum <- sai %>%
  group_by(item_no) %>%
  summarise(year_total = sum(sold), .groups = "drop")

sai <- left_join(sai, inventory_sum, by = c("item_no"))

###
# calculate the top 10% threshold
top_10_threshold <- quantile(sai$year_total, 0.9)

# dummy variable for bestsellers 1= yes 0 = no
sai <- sai %>% 
  mutate(best_seller = ifelse(year_total >= top_10_threshold, 1, 0))

### figure out month an year for data, assuming the data is from  2022
#week 0: December 27, 2021 - January 2, 2022
#week 52: December 19, 2022 - December 25, 2022
#week 53: December 26, 2022 - January 1, 2023

sai$year <- 2022
# find the year the week ends in, so we can figure out months
sai <- sai %>%
  mutate(wk_ending_year = ifelse(week %in% c(0, 53), year + 1, year),
         week = ifelse(week == 0, 52, ifelse(week == 53, 1, week)))


# create teh data and extract the month
# wanted month to be quantitative to reduce model complexity 

sai$date <- MMWRweek2Date(sai$wk_ending_year, sai$week)
sai$month <- month(sai$date, label = TRUE)
sai$month <- month(sai$date)






# create lag periods
# https://www.youtube.com/watch?v=Kn3llTjYS5E

sai <- sai %>%
  mutate(lag1 = lag(sold, 1),
         lag2 = lag(sold, 2))
```


create a model based on the best selling item for reasons XYZ
```{r}
a5i <-  sai %>% 
  filter(item_no == "A510004") %>% 
    select(month,
         week,
         month,
         sold,
         lag2,
         lag1)

# rolling average
# https://www.rdocumentation.org/packages/zoo/versions/1.8-12/topics/rollmean
a5i <- a5i %>% 
  mutate(moving_avg_4weeks = zoo::rollmean(sold, k = 4, fill = NA, align = "right"))


```

## Model Evaluation

find the best model using stepwise selection find the 2 best methods for every size predictors

```{r message=FALSE, warning=FALSE}

# https://youtu.be/IScjygOnO0w
set.seed(3746)
# forward Stepwise Selection
# nvmax = 8 specifies the maximum number of predictors to incorporate in the model.
a5i_mod <- regsubsets(sold ~  .,
                       data = a5i, nbest = 2, method = "exhaustive")
a5i_mod_summary_mx <- with(summary(a5i_mod), data.frame(rsq,adjr2, cp, rss, outmat))

a5i_mod_summary_mx$predictors_cnt <- c(1,1,2,2,3,3,4,4,5) # for graphing
a5i_mod_summary_mx$model <- c('a','b','a','b','a','b','a','b','a') # for graphing

# insert the num_predictors column to a5i_mod_summary_mx
a5i_mod_summary_mx 

```

```{r}
a5i_mod_summary_mx %>% 
  pivot_longer(c(adjr2, cp), names_to = "metric", values_to = "value") %>%
  ggplot(aes(x = predictors_cnt, y = value, color = model)) +
  geom_line(show.legend = F) +
  geom_point() +
  facet_wrap(~metric, scales = "free") +
  scale_x_continuous(breaks = 1:5)
```

# show the models in a table

explain why this is the best one

what do each of these things tell me? - rsq -\> highest r squared - adjr2 - \> highest - cp -\> smallest cp - rss -\> smallest

having trouble choosing, i spent a lot of time making my variables so lets look at AIC several models what is AIC? Lower AIC values indicate a better-fit model, and a model with a delta-AIC (the difference between the two AIC values being compared) of more than -2 is considered significantly better than the model it is being compared to

find the coefficients and AIC

```{r}
mod_compare <-  a5i_mod_summary_mx %>% 
  filter(model == "a",
         predictors_cnt >2) %>% 
  select(predictors_cnt,
          rsq,
          adjr2,
          cp,
          rss)


# best adjusted r squared 5 predictors 
mod5 <-  lm(sold~ month + week + lag1 + lag2 + moving_avg_4weeks, data = a5i)
mod5_aic <- AIC(mod5)


# mix of cp and adjusted r squared model a
mod4 <-  lm(sold~ month + lag1 + lag2 + moving_avg_4weeks, data = a5i)
mod4_aic <- AIC(mod4)

# best cp model a
mod3 <-  lm(sold~ lag1 + lag2 + moving_avg_4weeks, data = a5i)
mod3_aic <- AIC(mod3)


mod_compare$AIC <-  c(mod3_aic,mod4_aic, mod5_aic )
```

show the aic comparisons model 3 is the best, which makes the most sense since the other variables were not significant

lag 1 and 2 are the best along with rolling monthly average

next up, how can i apply a monthly rolling average to each invetory item??

# next up, how can u split the data without changing the weeks?

I can split it up by inventory??

add back in the best sellers and compare AICs?
