---
title: "Map making"
format: 
  html:
    code-fold: true
editor: visual
---

\[insert visual aid\]

## Overview of data

### The Walkability Index:

"dataset characterizes every Census 2019 block group in the U.S. based on upon characteristics of the built environment that influence the likelihood of walking being used as a mode of travel.\

## Geography

"The **Grand Rapids -- Kentwood -- Muskegon Combined Statistical Area** is the 2nd largest [CSA](https://en.wikipedia.org/wiki/Combined_statistical_area "Combined statistical area") in the [U.S. state](https://en.wikipedia.org/wiki/U.S._state "U.S. state") of [Michigan](https://en.wikipedia.org/wiki/Michigan "Michigan") (behind [Metro Detroit](https://en.wikipedia.org/wiki/Metro_Detroit "Metro Detroit")). The CSA had a population of 1,320,064 at the 2010 census. The primary cultural and financial centers of the region are [Grand Rapids](https://en.wikipedia.org/wiki/Grand_Rapids,_Michigan "Grand Rapids, Michigan"), [Muskegon](https://en.wikipedia.org/wiki/Muskegon,_Michigan "Muskegon, Michigan") and [Holland](https://en.wikipedia.org/wiki/Holland,_Michigan "Holland, Michigan"). It includes the four counties in the Grand Rapids-Kentwood MSA plus one [metropolitan area](https://en.wikipedia.org/wiki/United_States_metropolitan_area), adding the Muskegon, MI MSA of [Muskegon County](https://en.wikipedia.org/wiki/Muskegon_County,_Michigan "Muskegon County, Michigan"), and two [micropolitan areas](https://en.wikipedia.org/wiki/United_States_micropolitan_area "United States micropolitan area") of Holland of [Allegan County](https://en.wikipedia.org/wiki/Allegan_County "Allegan County"), and Big Rapids of [Mecosta County](https://en.wikipedia.org/wiki/Mecosta_County "Mecosta County") for a total of seven counties.

The Grand Rapids metropolitan area is part of the [Great Lakes Megalopolis](https://en.wikipedia.org/wiki/Great_Lakes_Megalopolis "Great Lakes Megalopolis") containing an estimated 54 million people."

there are 70 census tracts in the city of grand rapids

```{r include=FALSE}
#Import cleaned data from SQL and Census
source("~/gvsu/summer 23/stat 631/portfolio/Website/sections/dataviz/map/import_clean_merge.R")
```

```{r include=FALSE}

#import cleaned data
#Import cleaned data from SQL and Census
# source("~/map/import_clean_merge.R")

# map areas
my_state <-  'MI'
my_county <-  c("Kent")

roads_data <-  primary_secondary_roads(my_state) %>% 
  filter(RTTYP %in% c('U','S','I')) #this will limit the roads to just highways. 

landmass_data <-  counties(cb = TRUE, state = my_state) %>%
  filter(NAME %in% my_county)

water_data <-  area_water(my_state, my_county)

# Ensure the CRS for all objects are the same before performing spatial operations
map_area <-  st_crs(is_kent)

roads_data <- st_transform(roads_data, map_area)
landmass_data <- st_transform(landmass_data, map_area)
water_data <- st_transform(water_data, map_area)

grcty_map <- ggplot() +
  theme_void()  + #whiteout
  # blank gray map
  geom_sf(data = landmass_data, fill = '#e6e6e6', color = NA,aes(geometry = geometry))+
  #add walkability scores
  geom_sf(data = wlk_grcty, color = NA, aes(geometry = geometry, fill = NatWalkInd))+
  #add water
  geom_sf(data = water_data, fill = '#cce6ff',color = NA, aes(geometry = geometry)) +
  #add roads
  geom_sf(data = roads_data, color = 'white', aes(geometry = geometry))


# creates coordinates around the geographic area for a zoomed in map!
limits = st_bbox(wlk_grcty$geometry)
limits

grcty_map = grcty_map + 
  coord_sf(xlim = c(as.numeric(limits$xmin),as.numeric(limits$xmax)), 
           ylim = c(as.numeric(limits$ymin),as.numeric(limits$ymax))) +
  labs(fill = 'Walkability Index',
  title =  "Walkability in the Greater Grand Rapids Area",
  caption = "Source: 'The Walkability Index' | US Environmental Protection Agency") + 
  # move legend to bottom left
  theme(legend.justification = c(0,0), legend.position = c(5., 5.)) + 
  scale_fill_gradient(low = '#F1FCAE', high = '#184F50')

#super proud of my map :-) 
```


```{r echo=FALSE}
grcty_map
# Gr and it's immediate suburbs
# cenus blocks 06:19
```

###### inspired by Matt Bartholomew's "[Making a Better Map](https://bartholomatt.net/posts/census_maps_part2/), ggplot and Tigris"
