---
title: "Current Level of Understanding"
subtitle: "Statistical Modeling and Regression" 
format: html
editor: visual
execute:
  echo: false
---

![*Figure above represents aggregation of my self-assessed level of understanding on concepts presented in "[Introduction to Statistical Learning](https://www.statlearning.com/){target="_blank"}" and "[Data Feminism](https://data-feminism.mitpress.mit.edu/){target="_blank"}"*.](images/knowledge_stellar.png)

```{r message=FALSE, warning=FALSE,results = "hide"}
library(tidyverse)
library(gt) # table
library(paletteer)

```

```{r}
assess <-  read.csv("~/gvsu/summer 23/stat 631/Collection/sections/reflections/knowledge/assessment.csv")
assess_data <- assess %>% 
  rename(
    `Chapter Title` = Chapter.Title,
    `Section Title` = Section.Title,
    `Self Assessment` = Self.Assessment
  ) 

assess <- assess_data %>%
  mutate(Week = as.Date(Week, format = "%m/%d/%Y")) %>%
  filter(Week != as.Date("2023-06-26")) %>% # remove the duplicated year
  select("Book", "Section", "Section Title", "Self Assessment")
   

```

## Explanation of Assessment

#### **Proficient Areas:**

I marked items here as proficient because I have had repeated academic exposure and application of these concepts.

-   **Linear regression:**

    -   I have a basic understanding of the underlying concepts, assumptions, and techniques involved in linear regression. I have completed assignments and projects that required implementing linear regression and analyzing the results.

        -   For example, in my final project last semester in CIS 631, I conducted an analysis using multiple linear regression. The project focused on evaluating the relationship between crime rates and the presence of cannabis dispensaries while controlling for socioeconomic factors. I collected relevant data, preprocessed it, and applied multiple linear regression to model the relationship. I carefully interpreted the results and drew meaningful conclusions based on statistical significance and the summary of my model's output.

    -   Overall, my proficiency in linear regression is based on a combination of theoretical knowledge gained through coursework, practical application in projects and assignments, and the ability to critically analyze and interpret the results obtained.

#### **Aware Areas:**

I marked these items as aware because I am familiar with the terms,  but have limited practice applying the techniques.

-   **Data Feminism:**

    -   My awareness here derives from a combination of the literature and media I consume, along with principles discussed in PSM 650 -- "Ethical and professionalism" and CIS 631-- "Data Mining".

    -   I'd like to note that I bought the audiobook version of Data Feminism over Memorial Day. I am finding it easier to digest the philosophy presented in that format. 

-   **Classification:**

    -   I am familiar with the terms in classification and the types of ways we can categorize data as ordinal, nominal and categorical. I've used K-nearest neighbors algorithms, and decision trees in CIS 500 -- "Fundamentals of Software Practice."  I recognize I need to more exposure and practice here.

-   **Linear Model Selection and Regularization:**

    -   Looking over the section titles of this ISL chapter, I see I have had some practice with dimension reduction using principle component analysis but have not taken the opportunity to apply this methodology outside of a lab exercise.

    -   Additionally, as part of your Stat 518 -- Statistical Computing and Graphics with R, I deployed bootstrapping methodology in the final project.

-   **Multiple Testing:**

    -   I have had exposure to these concepts both professionally, when communicating market research and survey results and academically, particularly in Stat 216. I feel most comfortable with hypothesis testing , understanding type 1 and type 2 errors, and evaluating and explaining p-values.

    -   I marked this one as aware verses proficient because I feel I need more reinforcement learning in this area.

## Detailed Self-Assessment

```{r}

assess %>% 
 gt(rowname_col = "Book") %>%
  tab_header(title = md("Course Concepts")) %>% 
  cols_align(align = "left") %>% 
  data_color(
    columns = `Self Assessment`,
    palette = c("#15050B", "#F6D5E2","#D35C9E" ),
    domain = c(0, 3),
    alpha = 0.8
  )  %>% 
  
    tab_footnote(
    footnote = "Proficiency level ranges from 1 (low) to 3 (high).",
    locations = cells_column_labels(columns = `Self Assessment`)
  ) %>% 
    tab_options(
    grand_summary_row.background.color = "#D35C9E",
    heading.background.color = "#EFFBFC",
    column_labels.background.color = "#EFFBFC",
    stub.background.color = "#EFFBFC",
    table.font.color = "#323232",
    stub.border.style = "dashed",
    stub.border.width = "1px",
    table.width = "60%"
  ) %>%
  opt_all_caps()


#https://posit.co/blog/great-looking-tables-gt-0-2/

```
